\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-06-25 chapters/1_intro.tex
Add test results cityscapes
Delete comments

\section{Introduction}
In computer vision, the partitioning of weighted graphs has been successfully applied to such tasks as image segmentation, object tracking and pose estimation. %image segmentation, object tracking, stereo matching, etc.), to high-level tasks (e.g. image classification, object recognition, image parsing
% to model many types of re- lations and processes in physical, biological, social and information systems
Most graph clustering methods work with positive edge weights only, which can be interpreted as similarities or distances between the nodes. These methods are parameter-based and require users to specify the desired numbers of clusters or a termination criterion (e.g. spectral clustering or iterated normalized cuts) or even to add a seed for each object  (e.g. seeded watershed or random walker).  
%Hierarchical clustering is a popular graph clustering method, which creates a hierarchy of clusters. Hierarchical agglomerative clustering (HAC) is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy \cite{lance1967general}. This method usually requires the user to choose a level in the cluster hierarchy defining the desired output clustering.

@@

%Despite their similarity to agglomerative HC algorithms for unsigned graphs with only positive weights, neither an explicit connection nor a clear experimental comparison was proposed so far.

In this paper, we propose a novel theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering on positive-weighted graphs \cite{lance1967general}. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}. %, i.e. mutual exclusion between clusters. 
We then formally prove that some of the combinations correspond to existing clustering algorithms and introduce new algorithms for combinations which have not been explored yet. % The framework can also be easily expended to accommodate additional linkage criteria.
%As a first contribution, we reformulate several of these recently proposed graph agglomerative algorithms in a simple review framework (Sec. \ref{sec:general_framework}) that represents a generalization of agglomerative HC to graphs with both attractive and repulsive edge weights (see Figure \ref{fig:intro_figure} for a visual abstract). From this new point of view, agglomerative HC and algorithms proposed in \cite{levinkov2017comparative,wolf2018mutex,lance1967general,kardoostsolving} all share a general procedure but differ in the way inter-cluster interaction is updated after each iteration (Table \ref{tab:linkage-criteria}). At the same time, we also show that this framework allows us to introduce totally new variations of these algorithms. 
%Ultimately, by presenting this simple general approach, our hope is to motivate a deeper understanding of the connection between algorithms for unsigned and signed graphs.

We evaluate and compare these algorithms on \emph{instance segmentation} - a computer vision task of assigning each pixel of an image to an object instance. %, where the number of instances is usually not known in advance. 
We use a CNN to predict the edge weights of a graph such that each node represents a pixel of the image, similarly to \cite{liu2018affinity,lee2017superhuman,wolf2018mutex}, and provide these weights as input to the algorithms in our framework (see Fig. \ref{fig:intro_figure}). 
% For our experiments, we focus on a \emph{proposal-free} deep learning method that does not involve object detection but directly group pixels into object instances. 
%  (for example in electron microscopy (EM) image volumes of neurons \cite{arganda2015crowdsourcing})

With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms the previously known agglomeration methods expressed in the framework. It also achieves competitive performance on the challenging CREMI 2016 segmentation benchmark.
% This simple agglomerative algorithm also achieves competitive scores on the challenging CREMI 2016 segmentation benchmark, similarly to other approaches that rely on complex multi-step pipelines.

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/intro_image_v3.pdf} % left bottom right top
\caption{ Pipeline description: \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge. \textbf{(2)} Some short- and long-range predictions of our CNN model, where white pixels represent boundary evidence. \textbf{(3)} Outputs of two agglomerative algorithms included in our proposed generalized clustering framework, with \emph{Sum} and \emph{Average} linkage criteria. The final clustering / instance segmentation is shown in 3a, overlaid with the raw image.  The  agglomeration order in 3b shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black). (\textbf{4}) Some iterations of \algname{} on toy graph examples with attractive/positive (green) and repulsive/negative (red) interactions. At each iteration, the yellow edge with highest interaction is contracted (orange arrows), until only negative edges are left in the graph.
%We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 
% On the left: a single cluster is returned with only attractive interactions.
 % main ideas and contributions
\label{fig:intro_figure}}
\end{figure}

>>>>

\section{Introduction}
In computer vision, the partitioning of weighted graphs has been successfully applied to such tasks as image segmentation, object tracking and pose estimation. 
Most graph clustering methods work with positive edge weights only, which can be interpreted as similarities or distances between the nodes. These methods are parameter-based and require users to specify the desired numbers of clusters or a termination criterion (e.g. spectral clustering or iterated normalized cuts) or even to add a seed for each object  (e.g. seeded watershed or random walker).

@@

In this paper, we propose a novel theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering on positive-weighted graphs \cite{lance1967general}. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}. 
We then formally prove that some of the combinations correspond to existing clustering algorithms and introduce new algorithms for combinations which have not been explored yet.

We evaluate and compare these algorithms on \emph{instance segmentation} - a computer vision task of assigning each pixel of an image to an object instance. 
We use a CNN to predict the edge weights of a graph such that each node represents a pixel of the image, similarly to \cite{liu2018affinity,lee2017superhuman,wolf2018mutex}, and provide these weights as input to the algorithms in our framework (see Fig. \ref{fig:intro_figure}).

With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms the previously known agglomeration methods expressed in the framework. It also achieves competitive performance on the challenging CREMI 2016 segmentation benchmark and is state-of-the-art on CityScapes when compared to other proposal-free methods.
Our code is available at \url{https://github.com/abailoni/GASP}.

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth]{./figs/intro_image_v3.pdf} % left bottom right top
\caption{ Pipeline description: \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge. \textbf{(2)} Some short- and long-range predictions of our CNN model, where white pixels represent boundary evidence. \textbf{(3)} Outputs of two agglomerative algorithms included in our proposed generalized clustering framework, with \emph{Sum} and \emph{Average} linkage criteria. The final clustering / instance segmentation is shown in 3a, overlaid with the raw image.  The  agglomeration order in 3b shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black). (\textbf{4}) Some iterations of \algname{} on toy graph examples with attractive/positive (green) and repulsive/negative (red) interactions. At each iteration, the yellow edge with highest interaction is contracted (orange arrows), until only negative edges are left in the graph.
\label{fig:intro_figure}}
\end{figure}

### 2019-06-25 chapters/2_rel_work.tex
Delete comments

\section{Related work} \label{sec:related_work}
% Recent progress in semantic segmentation \cite{long2015fully,kong2018recurrent,chen2018deeplab}, boundary detection \cite{arbelaez2011contour,xie2015holistically,maninis2018convolutional}, %, optical flow \cite{weinzaepfel2013deepflow,dosovitskiy2015flownet},
% and pose estimation \cite{wei2016convolutional,cao2017realtime} was mostly associated with new key ideas and architectures in deep learning, like dilated convolutions \cite{yu2015multi,chen2018deeplab} or ``hourglass'' architectures with skip connections \cite{ronneberger2015u,paszke2016enet} increasing the receptive field of view of the model.
\textbf{Proposal-based methods} have been highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}. They decompose the instance segmentation task into two steps that consists in generating object proposals and assigning to each bounding box a class and a binary segmentation mask \cite{he2017mask,liu2018path,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}. 
% Here I could have more: \cite{pinheiro2015learning,pinheiro2016learning,hu2017fastmask} and probably something more in Deep coloring
% \item \emph{More references:} or generate generic proposal segments and then label each one with a semantic detector \cite{hariharan2014simultaneous,chen2015multi,hariharan2015hypercolumns,dai2015convolutional,uhrig2016pixel,he2017mask}.
They commonly rely on {Faster-RCNN}~\cite{ren2015faster} and can be trained end-to-end using non-maximum suppression. Other methods use instead recurrent models to sequentially generate instances one-by-one \cite{romera2016recurrent,ren2017end}.

\textbf{Proposal-free methods} adopt a bottom-up approach by directly grouping pixels into instances. Recently, there has been a growing interest for such  methods that do not involve object detection, since, in certain types of data, object instances cannot be approximated by bounding boxes. For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation; SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
% encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; 
a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction, whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,kulikov2018instance}. % Semi-convolutiona: \cite{novotny2018semi}
% \TODO{What about \cite{liang2018proposal} using spectral clustering?}. 
Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}.
%  and introducing a ﬁxed number of labels (colors) and then dynamically assigning object instances to those labels during training (coloring) \cite{kulikov2018instance}

\textbf{Edge detection} also experienced recent progress thanks to deep learning, both on natural images \cite{xie2015holistically,kokkinos2015pushing} and biological data \cite{lee2017superhuman,schmidt2018cell,meirovitch2016multi,ciresan2012deep}. In neuron segmentation for connectomics, a field of neuroscience we also address in our experiments, boundaries are converted to final instances with subsequent postprocessing and superpixel-merging:
% CNNs were introduced to this application in \cite{jain2007supervised}, but further progress in deep learning and 
% the introduction of new architectures lead to a much more refined boundary detection. 
% or trained an end-to-end watershed region growing algorithm \cite{wolf2017learned}.  
% Subsequent postprocessing and superpixel-merging outputs final instances. 
some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy; the lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, while flood-filling networks \cite{januszewski2018high} eliminate superpixels by training a recurrent CNN to perform region growing one region at the time. A structured learning approach was also proposed in \cite{funke2018large,turaga2009maximin}.
% \SOURCE{SSHMT} Check Funke proposals

\textbf{Agglomerative graph clustering} has often been applied to instance segmentation \cite{ren2013image,liu2016image,salembier2000binary}, because of its efficiency as compared to other top-down approaches like graph cuts. 
Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold; the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters. 
% \TODO{Roman, Cocoons, Benjamin?}
The optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy, while other pipelines use classical HAC linkage criteria, e.g. average linkage \cite{liu2018affinity,lee2017superhuman}, median \cite{funke2018large} or a linkage learned by a random forest classifier \cite{nunez2013machine,knowles2016rhoananet}.

\textbf{Clustering of signed graphs} has the goal of partitioning a graph with both attractive and repulsive cues. Finding an optimally balanced partitioning has a long history in combinatorial optimization \cite{grotschel1989cutting,grotschel1990facets,chopra1993partition}. %and can be done without the need to specify a termination criterion. 
NP-hardness of the \emph{correlation clustering} problem was shown in \cite{bansal2004correlation}, while the connection with graph multicuts was made by \cite{demaine2006correlation}. Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy agglomerative algorithms \cite{levinkov2017comparative,wolf2019mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs.
% \TODO{Cannot-link constraints?}
% Missing: Funke proposals, discussion about cannot-link constraints!!!

>>>>

\section{Related work} \label{sec:related_work}
\textbf{Proposal-based methods} have been highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}. They decompose the instance segmentation task into two steps that consists in generating object proposals and assigning to each bounding box a class and a binary segmentation mask \cite{he2017mask,liu2018path,yang2012layered,li2017fully,ladicky2010and,hariharan2014simultaneous,chen2015multi,dai2016instance,liang2016reversible}. 
They commonly rely on {Faster-RCNN}~\cite{ren2015faster} and can be trained end-to-end using non-maximum suppression. Other methods use instead recurrent models to sequentially generate instances one-by-one \cite{romera2016recurrent,ren2017end}.

\textbf{Proposal-free methods} adopt a bottom-up approach by directly grouping pixels into instances. Recently, there has been a growing interest for such  methods that do not involve object detection, since, in certain types of data, object instances cannot be approximated by bounding boxes. For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation; SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction, whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,kulikov2018instance}. 
Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}.

\textbf{Edge detection} also experienced recent progress thanks to deep learning, both on natural images \cite{xie2015holistically,kokkinos2015pushing} and biological data \cite{lee2017superhuman,schmidt2018cell,meirovitch2016multi,ciresan2012deep}. In neuron segmentation for connectomics, a field of neuroscience we also address in our experiments, boundaries are converted to final instances with subsequent postprocessing and superpixel-merging:
some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy; the lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, while flood-filling networks \cite{januszewski2018high} eliminate superpixels by training a recurrent CNN to perform region growing one region at the time. A structured learning approach was also proposed in \cite{funke2018large,turaga2009maximin}.

\textbf{Agglomerative graph clustering} has often been applied to instance segmentation \cite{ren2013image,liu2016image,salembier2000binary}, because of its efficiency as compared to other top-down approaches like graph cuts. 
Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold; the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters. 
The optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy, while other pipelines use classical HAC linkage criteria, e.g. average linkage \cite{liu2018affinity,lee2017superhuman}, median \cite{funke2018large} or a linkage learned by a random forest classifier \cite{nunez2013machine,knowles2016rhoananet}.

\textbf{Clustering of signed graphs} has the goal of partitioning a graph with both attractive and repulsive cues. Finding an optimally balanced partitioning has a long history in combinatorial optimization \cite{grotschel1989cutting,grotschel1990facets,chopra1993partition}. %and can be done without the need to specify a termination criterion. 
NP-hardness of the \emph{correlation clustering} problem was shown in \cite{bansal2004correlation}, while the connection with graph multicuts was made by \cite{demaine2006correlation}. Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy agglomerative algorithms \cite{levinkov2017comparative,wolf2019mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs.
